---
title: "vgpd Data Collection and Processing"
author: "Brian Waismeyer"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vgpd Data Collection and Processing}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This document is a record of how the data included with the \code{vgpd} package 
was produced (and how it can be updated). It will point you - the reader -  to
all necessary package code, demonstrate its use, and describe the results you
should expect.

The objective of this code is to create a dataset of video games and their
protagonists.

This dataset is created by pulling together several sources of data:

* [Steam API]():
* [Steam Spy API]():
* [protagonist data]():
* ...

## Warning: You Probably Don't Want to Run This Code

Little of the code in this vignette was run when the vignette was produced.
You'll see that much of the code was commented out and this was intentional.

Some of the data collection - especially the data extracted from the Steam API -
is extremely time intensive. To save you time and get you into the data more
quickly, the major building blocks and final drafts of the \code{vgpd} datasets
have been included in this package.

This document will use these in-built data objects to illustrate the results
of the data gathering and cleaning code. When you are ready to work with the
data, you are encouraged to use the provided data either as-is or as a
foundation for updates.

## Supporting Packages

All supporting packages should have been installed along with the \code{vgpd}
package. 

```{r load_packages}
# If you haven't already, you should install the vgpd package. The simplest
# way to do this is with devtools.

# NOT RUN
# devtools::install_github("bwaismeyer/vg_demographics", subdir = "vpgd")

# Once installed, vgpd should include all the resources needed to create,
# load, or update the package data.
library(vgpd)

# We'll also load some additional packages to support the demonstrations in
# this vignette.
library(dplyr)
library(tidyr)
library(stringr)
library(jsonlite)
```

## Step 1: Creating the `steam_app_list`

```{r load_package_data}
# We load the in-built package data to illustrate what the Steam API code
# should produce and to illustrate how we go from the early raw download
# to a clean dataframe.
data("steam_app_list")
```

```{r process_raw_data}
# Next we process the raw data into an intermediate dataframe.
raw_df <- flatten_lists_to_df(steam_app_list)
```

```{r clean_raw_df}
# Next we examine the resulting dataframe. It has a lot of variables so we avoid
# print-heavy functions (e.g., str, summary).
dim(raw_df)
head(names(raw_df))

# We inspect the dataframe for missing values.
raw_df %>%
    apply(2, function(x) {sum(is.na(x))}) %>%
    sort() %>%
    head(20)

# We see immediately a high number of missing values for everything but 
# success. This makes more sense when we look at the distribution for success.
table(raw_df$success)

# App queries that returned success == FALSE are dummy records. It's unclear why
# they exist (perhaps old Steam apps?), but they can be discarded as useless
# for our purposes as they have no data at all.
rs_df <- raw_df %>%
    filter(success == "TRUE")

# We check our missing values again.    
rs_df %>%
    apply(2, function(x) {sum(is.na(x))}) %>%
    sort() %>%
    head(20)
```
